%-------------------------
% Resume in Latex
% Author : Shubham Chadokar
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\ifdefined\pdfgentounicode\pdfgentounicode=1\fi

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Shubham Chadokar} \\ \vspace{8pt}
    \small 8649904058 $|$ \href{mailto:shubhamchadokar04@gmail.com}{\underline{shubhamchadokar04@gmail.com}} $|$
    \href{https://linkedin.com/in/schadokar}{\underline{linkedin.com/in/schadokar}} $|$
    \href{https://github.com/schadokar}{\underline{github.com/schadokar}} $|$
    \href{https://schadokar.dev}{\underline{schadokar.dev}}
\end{center}

%-----------SUMMARY-----------
\vspace{-20pt}
\section{Summary}
\small{Backend platform engineer with 10 years of experience building systems at scale. Architected a CPaaS billing platform handling $\sim$1B txns/day at 10K RPS; consolidated a 20-service data pipeline into 5 components ($-75\%$ complexity, 5--6X throughput headroom); delivered a zero-downtime platform-wide SSO with zero production disruption. Core stack: Go, Kafka, Kubernetes, PostgreSQL; track record across architecture, delivery, on-call, and mentorship.}
\vspace{-12pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Infoblox}{Sept. 2024 -- Present}
      {Senior Software Engineer \textemdash{} Data Engineering}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Defined and drove adoption of a new Cloud Data Connector architecture, consolidating 20 microservices into 5 modular components ($-75\%$ complexity); benchmarks validated 5--6X throughput headroom, establishing the design as the platform's scalability foundation for the next growth phase.}
        \resumeItem{Identified an emerging Kafka topic-explosion risk before it manifested \textemdash{} led the technical design and cross-team alignment on a per-customer keyed partition topology, cutting projected topic count 100X (1M $\rightarrow$ 10K); enforced broker-level tenant isolation with a zero-downtime migration, protecting scalability headroom for 1K$\rightarrow$10K customer growth.}
        \resumeItem{Improved end-to-end pipeline latency and throughput 60--70\% by profiling Go services, refactoring critical code paths, and eliminating redundant processing layers.}
        \resumeItem{Rebuilt Grafana observability and alerting infrastructure from scratch across 5 services \textemdash{} reduced MTTD on customer-impacting incidents from $\sim$4 hrs to 20 min; established SLO dashboards and on-call runbooks adopted as team standard.}
        \resumeItem{Independently designed and shipped 3 internal LLM agents (PR review, deployment automation, sprint retros), later adopted across the engineering team \textemdash{} reclaimed $\sim$2 hrs/week per engineer in aggregate and eliminated deploy failures from manual misconfiguration entirely (0 incidents in 3 months post-launch).}
      \resumeItemListEnd

    \resumeSubheading
      {Kaleyra (Tata Communications)}{Apr. 2021 -- Oct. 2023}
      {Associate Software Architect \textemdash{} Billing, SSO, Chat Platform}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Designed and delivered the CPaaS billing platform end-to-end \textemdash{} 10K RPS, $\sim$1B transactions/day \textemdash{} leading 3 engineers across architecture, breakdown, reviews, and release.}
        \resumeItem{Cut billing latency by 60\% and infrastructure cost by 30\% by redesigning service architecture and data flows; reduced compute footprint 10X via high-frequency transaction batching.}
        \resumeItem{Resolved recurring MongoDB file descriptor outages (2--3/month at peak) across 10 services by designing a tier-based collection model \textemdash{} reducing 100K+ collections to a manageable pool, coordinated across 4 teams and validated by MongoDB consultants \textemdash{} directly enabling a new premium revenue tier (faster reports + extended data retention).}
        \resumeItem{Delivered a zero-disruption rollout of a platform-wide Keycloak SSO gateway affecting every engineer, team, and customer \textemdash{} a zero-downtime system where any failure would cause company-wide outage \textemdash{} zero production incidents during and after launch; architected the integration, defined the cutover sequence, and coordinated delivery across 2 engineers.}
        \resumeItem{Eliminated a cross-departmental approval bottleneck by designing and implementing a company-level admin SSO \textemdash{} collapsed recursive approval chains spanning 3 departments into a single-step process; led 2 engineers end-to-end.}
        \resumeItem{Rewrote the WhatsApp Web-style chat platform from scratch in Go and migrated SQL $\rightarrow$ MongoDB, eliminating class-level reliability bugs and removing the relational-schema scaling ceiling.}
        \resumeItem{Migrated legacy PHP billing service to Go and admin portals to Node.js, cutting tech debt by $70$--$80\%$ and improving load performance by $80$--$90\%$.}
        \resumeItem{Mentored 3 junior engineers on distributed-systems design \textemdash{} outcomes: 1 promoted to Senior SWE, 1 joined Amazon, 1 admitted to IIT (M.Tech).}
      \resumeItemListEnd

    \resumeSubheading
      {Deloitte}{Mar. 2020 -- Apr. 2021}
      {Solution Advisor \textemdash{} Blockchain \& Digital Assets}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Refactored critical execution paths in a blockchain custody platform for enterprise clients, achieving 20\% throughput gain and eliminating manual audit overhead through automated custody verification; contributed technical risk assessment for Facebook Novi infrastructure.}
      \resumeItemListEnd

    \resumeSubheading
      {MSR Cosmos}{Aug. 2018 -- Mar. 2020}
      {Software Engineer \textemdash{} Blockchain}{Hyderabad, India}

    \vspace{4pt}
    \resumeSubheading
      {Infosys}{Jun. 2016 -- Aug. 2018}
      {System Engineer \textemdash{} Blockchain R\&D}{Bangalore, India}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Munshiji} $|$ \href{https://munshiji.xyz}{\underline{munshiji.xyz}}}{}
          \resumeItemListStart
            \resumeItem{Open-source, self-hosted personal finance dashboard built for India \textemdash{} first-class support for EPF, NPS, PPF, SSY, and 13+ Indian account types that global tools don't model.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Writing \& Speaking} $|$ \emph{freeCodeCamp, Towards Data Science, DigitalOcean, schadokar.dev}}{}
          \resumeItemListStart
            \resumeItem{Author of \emph{Playtime with Hyperledger Composer} (eBook)}
            \resumeItem{Speaker at London Gophers, Pune Gophers, and DockerCon on Go, distributed systems, and container tooling.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Jabalpur Engineering College}{Jabalpur, MP}
      {Bachelor of Engineering, Electronics and Telecommunication}{Aug. 2012 -- May 2016}
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go, JavaScript, Python, SQL, C\#} \\
     \textbf{Infra \& Data}{: Kubernetes, Docker, AWS, GCP, Azure, Kafka, PostgreSQL, MongoDB, MySQL, Redis, RabbitMQ} \\
     \textbf{Frameworks \& Tools}{: gRPC, REST, Node.js, ReactJS, Keycloak, Grafana}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
